---
title: "Recovery Model Retraining"
date: today
date-format: "YYYY-MM-DD HH:mm z"
format:
  html:
    embed-resources: true
    code-fold: true
    toc: true
execute:
  echo: true
  warning: false
  message: false
---

Retrains the multi-stage bootstrap recovery model on the latest committed `recovery_primitives` pin and publishes a versioned `recovery_model` artifact. Scheduled weekly via GitHub Actions.

## Setup

```{r}
library(here)
library(pins)
library(digest)
source(here::here("R", "recovery_model.R"))

board <- board_folder(here::here("data", "pins"), versioned = TRUE)
```

## Read upstream primitives

```{r}
primitives    <- pin_read(board, "recovery_primitives")
upstream_hash <- substr(digest(primitives, algo = "sha256"), 1, 12)

knitr::kable(data.frame(
  metric = c("Total batches", "Completed batches", "Termination rate",
             "Date range", "Upstream hash"),
  value  = c(
    nrow(primitives),
    sum(primitives$outcome_status == "Completed"),
    sprintf("%.1f%%", 100 * mean(primitives$outcome_status == "Terminated")),
    paste(format(min(primitives$collection_date)),
          format(max(primitives$collection_date)), sep = " to "),
    upstream_hash
  )
))
```

## Train

```{r}
model <- new_recovery_model(
  primitives,
  reference_date = max(primitives$collection_date),
  decay_tau_days = 180,
  upstream_hash  = upstream_hash
)
model
```

Time-decay weighting reduces the effective sample size from `r model$n_pool`
completed batches to `r round(model$decay_ess, 1)`, emphasizing recent
batches to track non-stationarity in stage 3 recovery.

## Publish

```{r}
pin_write(
  board,
  model,
  name        = "recovery_model",
  type        = "rds",
  title       = "Multi-stage bootstrap recovery model",
  description = sprintf("Trained on %d completed batches; decay tau %d days; ESS %.1f.",
                        model$n_pool, model$decay_tau_days, model$decay_ess),
  metadata    = list(
    n_pool         = model$n_pool,
    decay_tau_days = model$decay_tau_days,
    decay_ess      = round(model$decay_ess, 2),
    reference_date = format(model$reference_date),
    upstream_hash  = model$upstream_hash,
    trained_on     = format(model$trained_on)
  )
)
```
