---
title: "Daily Batch Scoring"
date: today
date-format: "YYYY-MM-DD HH:mm z"
format:
  html:
    embed-resources: true
    code-fold: true
    toc: true
execute:
  echo: true
  warning: false
  message: false
---

Scores any primitives not yet seen under the current model and appends them to
`predictions_history`. Idempotent on `(batch_id, model_pin_hash)`: a retrain
produces a new model hash, which triggers re-scoring of every batch under the
fresh model. Scheduled daily via GitHub Actions.

## Setup

```{r}
library(here)
library(pins)
library(digest)
source(here::here("R", "recovery_model.R"))

board <- board_folder(here::here("data", "pins"), versioned = TRUE)
```

## Load model + primitives

```{r}
model          <- pin_read(board, "recovery_model")
primitives     <- pin_read(board, "recovery_primitives")
model_pin_hash <- substr(digest(model, algo = "sha256"), 1, 12)
```

## Anti-join against history

```{r}
history <- tryCatch(pin_read(board, "predictions_history"),
                    error = function(e) NULL)

already_scored <- if (is.null(history)) character(0) else
  history$batch_id[history$model_pin_hash == model_pin_hash]

to_score <- primitives[!primitives$batch_id %in% already_scored, ]

knitr::kable(data.frame(
  metric = c("Model pin hash", "History rows", "Batches to score"),
  value  = c(model_pin_hash,
             if (is.null(history)) 0 else nrow(history),
             nrow(to_score))
))
```

## Score and append

```{r}
if (nrow(to_score) > 0) {
  preds <- predict_yield(model, to_score$input_cells, n_compound = 5000)

  new_history <- data.frame(
    batch_id        = to_score$batch_id,
    collection_date = to_score$collection_date,
    input_cells     = to_score$input_cells,
    q05             = preds$q05,
    q25             = preds$q25,
    q50             = preds$q50,
    q75             = preds$q75,
    q95             = preds$q95,
    model_pin_hash  = model_pin_hash,
    scored_at       = Sys.time(),
    stringsAsFactors = FALSE
  )

  combined <- if (is.null(history)) new_history else rbind(history, new_history)

  pin_write(
    board,
    combined,
    name        = "predictions_history",
    type        = "rds",
    title       = "Per-batch predictions appended over time",
    description = "Idempotent on (batch_id, model_pin_hash)."
  )
}
```

## Sample of new predictions

```{r}
if (nrow(to_score) > 0) {
  knitr::kable(head(new_history[, c("batch_id", "collection_date",
                                    "input_cells", "q25", "q50", "q75")], 10),
               digits = 3,
               caption = sprintf("First 10 of %d newly scored batches.",
                                 nrow(new_history)))
}
```
